---
title: Valid Covid Certificates in Austria
author: Sophie Steininger
date: '2021-05-12'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```


```{r, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE, results='hide',fig.keep='all', include=FALSE}
###Libraries
pacman::p_load(tidyverse, leaflet, sf, htmlwidgets, spdep)

##Read in the Vaccination data 

vac_data_intro <- read_delim("COVID19_vaccination_municipalities.csv", delim = ";")

##Geo Data 
new_geo_dat <- st_read("C:/Users/sophi/Documents/Dokumente final/UNI AKTUELLES/Economic and Social Policy - Data Science/Github HW/GeoJSON-TopoJSON-Austria/2021/simplified-95/gemeinden_95_geo.json")


##Transform and merge Data
tansformated <- vac_data_intro %>%
  mutate("iso" = as.character(municipality_id))

vac_data <- new_geo_dat %>%
  full_join(tansformated, by = "iso") 


##Bundesländer Data
new_geo_dat_laender <- st_read("C:/Users/sophi/Documents/Dokumente final/UNI AKTUELLES/Economic and Social Policy - Data Science/Github HW/GeoJSON-TopoJSON-Austria/2021/simplified-95/laender_95_geo.json")
             
#valid_percent_certificates
quantiles <- round(quantile(vac_data$valid_certificates_percent, na.rm = TRUE))
pal <- colorBin("Greens", 
                domain = vac_data$valid_certificates_percent, 
                bins = quantiles)

m <- leaflet(vac_data) %>%
  addProviderTiles("CartoDB") %>%
  setView(lat = 47.367538, lng = 13.436292, zoom = 6) %>%
  addPolygons(
    fillColor = ~pal(valid_certificates_percent),
    opacity = 0.2,
    weight = 0.5,
    color = "Black",
    fillOpacity = 0.7, 
    group = "Valid_Certificates_Percent", 
    popup = ~paste0("<b>", name, "</b>", 
                    "<br/>", round(valid_certificates_percent, digits = 2), "%"), 
    highlightOptions = highlightOptions(
      weight = 1,
      color = "red",
      bringToFront = TRUE))  %>% 
  addLegend(position = "topright", 
    pal = pal, 
    values = quantiles, 
    title = "Percentage of Valid Certificates",
    labFormat = labelFormat(suffix = "%", 
                            between = "% &ndash; "),
    group = "Valid_Certificates_Percent") %>%
  addPolygons(
    data = new_geo_dat_laender, 
    color = "black", 
    weight = 1, 
    fill = FALSE)

```
The map of Austria below visualizes the percentage of the population with a valid Covid Certificate. 
The bins are selected according to the quantiles of the distribution.  <br>
For the visualization I used the leaflet package, which creates interactive HTML outputs.

```{r, echo=FALSE}
m
```

The Data for the percentage of valid covid certificates for each Gemeinde was retrieved from https://www.data.gv.at/katalog/dataset/covid-19-impfdaten-auf-gemeindeebene/resource/23cb19ff-20cb-4f74-bf21-3c6dbccfb0b4.  <br>
The geo Data for Austrian municipialities was retrieved from https://data.statistik.gv.at/web/meta.jsp?dataset=OGDEXT_GEM_1. 
The data was last updated on Dec 05 2021. 
